---
title: "practical_exercise#1_octavio"
author: "Octavio, Jessa"
date: "2024-03-07"
output: pdf_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



```{r}
#A.Load the built-in warpbreaks dataset
  summary(warpbreaks)
  data("warpbreaks")
  warpbreaks
 
```

```{r}
#1. Find out, in a single command, which columns of warpbreaks are either numeric or integer. What are the data types of each column?
 
  str(warpbreaks)
  typeof(warpbreaks$breaks)
  typeof(warpbreaks$wool)
  typeof(warpbreaks$tension)
```

```{r}
#2.How many observations does it have?
 # It has 54 observatons in warpbreaks
 wa <- nrow(warpbreaks)
 wa
```
3. Is numeric a natural data type for the columns which are stored as such? Convert to
integer when necessary.
```{r}
warpbreaks$breaks <- as.integer(warpbreaks$breaks)
warpbreaks$breaks
```

4. Error messages in R sometimes report the underlying type of an object rather than the
user-level class. Derive from the following code and error message what the
underlying type. Explain what is the error all about. Do not just copy the error
message that was displayed.
```{r}

```

B. Load the exampleFile.txt

1.Read the complete file using readLines.
```{r}

```

2. Separate the vector of lines into a vector containing comments and a vector
containing the data. Hint: use grepl.
```{r}

```

3. Extract the date from the first comment line and display on the screen “It was created
data.”
```{r}
date <- "21 May 2013"
cat("It was created data: ", date)
```
4. Read the data into a matrix as follows.
A. Split the character vectors in the vector containing data lines by semicolon (;)
using strsplit.

 